Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-21 robdml.tex
tex

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Deep metric learning, being vulnerable to adversarial
	attacks, has safety and security implications in its applications.
	% 
	Owing to the significance of this issue, a series of defense methods
	are proposed to improve its adversarial robustness.
	% insight
	However, as a model with triplet loss is prone to collapse with
	excessively hard samples, the existing methods refrain from using the
	classical min-max adversarial training paradigm, and hence suffer from
	inefficient learning from a strong adversary.
	% our finding
	In this paper, we reveal a significant impact of triplet sampling strategy
	on the adversarial training.
	% solution 1
	Based on this, Hardness Manipulation is proposed to adversarially perturb
	a given triplet into a specified hardness level in min-max adversarial
	training, instead of creating hardest triplets rendering model collapse.
	% solution 2
	To further improve the model performance, we propose a Gradual
	Adversary to dynamicly change the hardness level to balance metric
	learning and adversarial learning.
	% Experiment
	The proposed method is validated on three commonly
	used deep metric learning datasets, namely CUB-200-2011, Cars-196,
	and Stanford Online Product.
	% Conclusion
	Comprehensive experimental results show our method outperforms
	the existing defense methods, while achieving clearly higher
	efficiency at a lower training cost.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
	% background
	Owing to the significance of the adversarial vulnerability of deep metric
	learning models, which poses safety and security implications in its
	applications, a series of defense methods have been proposed to improve its
	adversarial robustness.
	% insight
	In order to avoid model collapse due to excessively hard examples, the
	existing methods refrain from using the typical min-max adversarial
	training paradigm, but instead learn from a weak adversary.
	% our starting point
	However, we argue that a model can learn from a strong adversary without
	model collapse, where the key for overall performance is triplet hardness.
	% HM framework
	To this end, Hardness Manipulation is proposed to adversarially perturb
	the training triplet to increase its hardness into a specified level,
	by referencing other benign triplets, or a pseudo-hardness function.
	% GA Adversary
	To further improve the model performance, we propose a Gradual Adversary to
	dynamicly change the hardness level to balance metric learning and
	adversarial learning.
	% Experiment
	The proposed method is validated on three commonly used deep metric
	learning datasets, namely CUB-200-2011, Cars-196, and Stanford Online
	Product.
	% Conclusion
	Comprehensive experimental results show our method outperforms the existing
	defense methods, while achieving clearly higher efficiency at a lower
	training cost.  
%
\end{abstract}
